Selecting Computations: Theory and Applications

### 2012-08-13 paper/vago.uai/slides/slides.tex
slides in progress, mostly done

\begin{frame}{Upper Bounds on Value of Information}
\end{frame}

\begin{frame}{Sampling in Trees}
\begin{itemize}
\item Hybrid sampling scheme:
\begin{enumerate}
\item At the {\it root node}: sample based on the VOI estimate.
\item At {\it non-root nodes}: sample using UCT.
\end{enumerate}
\item Stopping Criterion
\end{itemize}
\end{frame}

\begin{frame}{Sample Redistribution}
\begin{itemize}
\item<+-> The VOI estimate assumes that the information is {\bf discarded}
  between states.
\item<+-> MCTS {\bf re-uses rollouts} generated at earlier search states.
\vspace{\baselineskip}
\item<+-> Either incorporate `future' influence into the VOI estimate
  ({\it non-trivial!}).
\item<+-> Or behave myopically w.r.t. search tree depth:
\begin{enumerate}
\item Estimate VOI as though the information is discarded.
\item Stop early if the VOI is below a certain threshold.
\item Save the unused sample budget for search in future states.
\end{enumerate}
\item<+-> The cost $c$ of a sample  is\\\hspace{1em} the VOI of increasing a
  future budget by one sample.
\end{itemize}
\end{frame}

>>>>

\begin{frame}{Upper Bounds on Value of Information}
Assuming that:
\begin{enumerate}
\item Samples are i.i.d. given the value of the arm.
\item The expectation of a selection in a belief state is equal to the sample mean.
\end{enumerate}
Upper bounds on intrinsic VOI $\Lambda^b_i$ of testing the $i$th arm N
times are (based on Hoeffding inequality):
\begin{align*}
  \Lambda&_\alpha^b < \frac {2N\overline X_\beta^{n_\beta}} {n_\alpha+1}\exp\left(- 1.37(\overline X_\alpha^{n_\alpha}\hspace{-0.5em} - \overline X_\beta^{n_\beta})^2 n_\alpha\right)\\
  \Lambda&_{i|i\ne\alpha}^b <  \frac {2N(1-\overline  X_\alpha^{n_\alpha})} {n_i+1}\exp\left(- 1.37(\overline X_\alpha^{n_\alpha}\hspace{-0.5em} - \overline X_i^{n_i})^2 n_i\right)
\end{align*}
Tighter bounds can be obtained (see the paper).

\end{frame}

\begin{frame}{Sampling in Trees}
\begin{itemize}
\item Hybrid sampling scheme:
\begin{enumerate}
\item At the {\it root node}: sample based on the VOI estimate.
\item At {\it non-root nodes}: sample using UCT.
\end{enumerate}
\item Stopping criterion: Assuming sample cost $c$ is known,\\
\hspace{1em}stop sampling when intrinsic VOI is less than $C=cN$:
\begin{align*}
\frac 1 N \Lambda_\alpha^b \le&\frac {\overline X_\beta^{n_\beta}}
  {n_\alpha+1}\Pr(\overline X_\alpha^{n_\alpha+N}\le\overline
  X_\beta^{n_\alpha})\le c\\
\frac 1 N \max_i\Lambda_i^b\le &\max_i\frac {(1-\overline X_\alpha^{n_\alpha})} {n_i+1}\Pr(\overline
  X_i^{n_i+N}\ge\overline X_\alpha^{n_\alpha})\le c\\
    &\forall i: i\ne\alpha
\end{align*}
\end{itemize}
\end{frame}

\begin{frame}{Sample Redistribution}
\begin{itemize}
\item The VOI estimate assumes that the information is {\bf discarded}
  between states.
\item MCTS {\bf re-uses rollouts} generated at earlier search states.
\vspace{\baselineskip}
\item Either incorporate `future' influence into the VOI estimate
  ({\it non-trivial!}).
\item Or behave myopically w.r.t. search tree depth:
\begin{enumerate}
\item Estimate VOI as though the information is discarded.
\item Stop early if the VOI is below a certain threshold.
\item Save the unused sample budget for search in future states.
\end{enumerate}
\item The cost $c$ of a sample  is\\\hspace{1em} the VOI of increasing a
  future budget by one sample.
\end{itemize}
\end{frame}
